RBE/CS549 Project: Boat Tracking/Detection

### 2017-12-15 paper/two_pager.tex
Add individual contributions
Wording tweaks and margin fix

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{subfigure}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\graphicspath{ {images/} }

@@

\begin{enumerate}
\item We read a frame of video and convert it to HSV space
\item Perform a slew of static transforms to try and determine,
      based on the content of a single frame, which areas are and
      are not water/sky/land/objects (see Figure \ref{fig:boatconf}:
  \begin{enumerate}
    \item We use a nonlinear k-means classification to
          identify non-water based areas
    \item And then use Matlab's \texttt{bwareaopen} to
          identify the connected areas of the sky
  \end{enumerate}
\item Use optical flow information from a given pair of frames to
      locate the moving objects in a frame, based on Matlab's
      \texttt{opticalFlowFarneback}, and a simple model of the
      expected flow of the water to filter out the background in
      the optical flow space, resulting in confidence scores
      as in Figure \ref{fig:diff_magnitude}
\item Combine the above to determine a set of viable blobs using erodes/dilates
      and Matlab's \texttt{bwlabel}
\item Associate the blobs with each other and with preexisting objects,
      creating new objects for blobs that can't be associated with any
      preexisting objects, based on:
  \begin{enumerate}
    \item Similarity in blob/object velocities
    \item Similarity of blob/object position
    \item Taking weighted averages of velocities to combine them, and
          combining the object bounding boxes
  \end{enumerate}
\item Update objects in preparation for the next frame, updating
      positions using velocities, reducing and increasing confidence
      scores as appropriate, deleting objects with sufficiently low
      scores
\end{enumerate}

\begin{figure}[H]
\includegraphics[width=7cm]{hsv_kmeans2_orig}
\includegraphics[width=7.5cm]{hsv_kmeans2_suppressed}
\centering
\caption{Boat Confidence Results}
\label{fig:boatconf}
\end{figure}

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage{chngcntr}
\counterwithin{figure}{section}
\graphicspath{ {images/} }

@@

\begin{enumerate}
\item We read a frame of video and convert it to HSV space
\item Perform a slew of static transforms to try and determine,
      based on the content of a single frame, which areas are and
      are not water/sky/land/objects (see Figure \ref{fig:boatconf}:
  \begin{enumerate}
    \item Use a 2-class k-means classification to
          identify non-water based areas
    \item Suppress wave reflections using squared cluster distance as confidence
    \item Use Matlab's \texttt{bwareaopen} to
          identify and suppress the connected areas of the sky
  \end{enumerate}
\item Use optical flow information from a given pair of frames to
      locate the moving objects in a frame, based on Matlab's
      \texttt{opticalFlowFarneback}, and a simple model of the
      expected flow of the water to filter out the background in
      the optical flow space, resulting in confidence scores
      as in Figure \ref{fig:diff_magnitude}
\item Combine the above to determine a set of viable blobs using erodes/dilates
      and Matlab's \texttt{bwlabel}
\item Associate the blobs with each other and with preexisting objects,
      creating new objects for blobs that can't be associated with any
      preexisting objects, based on:
  \begin{enumerate}
    \item Similarity in blob/object velocities
    \item Similarity of blob/object position
    \item Taking weighted averages of velocities to combine them, and
          combining the object bounding boxes
  \end{enumerate}
\item Update objects in preparation for the next frame, updating
      positions using velocities, reducing and increasing confidence
      scores as appropriate, deleting objects with sufficiently low
      scores
\end{enumerate}

\begin{figure}[H]
\includegraphics[width=7cm]{hsv_kmeans2_orig}
\includegraphics[width=7.5cm]{hsv_kmeans2_suppressed}
\centering
\caption{Segmentation Confidence Results}
\label{fig:boatconf}
\end{figure}

@@

\section{Individual Contributions}
Jordan Burklund
\begin{itemize}

\item Na\"ive K-means classifier
\item Water and sky suppression
\end{itemize}

James Kuszmaul
\begin{itemize}
\item Optical flow segmentation
\item Object blob association
\item Evaluation cost function
\end{itemize}
